---
title: "Tribe Outout"
author: "Emilio Pantoja"
date: '2024-05-28'
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

rm(list = ls())

Loading in libraries for tidying data and graphing

```{r setup, include=FALSE}

require(readr)
require(tidyverse)
require(knitr)
require(dplyr)
require(ggplot2)
require(cowplot)
require(patchwork)
require(caTools)
require(readxl)

```

Importing csv files containing data of tribes for Ultimatum Game and Dictator Game, respectively

```{r}

merged_new_UGdata <- read_csv("C:/Users/epant/Dropbox/My PC (MSI)/Downloads/merged_new_UGdata.csv")
ChatGPTOutput <- read_excel("C:/Users/epant/Dropbox/My PC (MSI)/Downloads/ChatGPTOutput.xlsx")

merged_newDGdata <- read_csv("C:/Users/epant/Dropbox/My PC (MSI)/Downloads/merged_newDGdata.csv")

```

Merge UG Tribe data with UG ChatGPT data

```{r}

UGdata = rbind(merged_new_UGdata, ChatGPTOutput)

```

Partitioning data such that the range of offer rates are constrained to lie between 1 and 9 (remove extremum)
Also, Create an additional dataset that contains only observations with offer amount 0 (for the dictator game)

```{r}

DGdata_Partitioned = merged_newDGdata[!(merged_newDGdata$`Offer Amount` %in% c(0,10)),] 
UGdata_Partitioned = UGdata[!(UGdata$`Offer Percentage` %in% c(0,10)),] 

DGdataZero <- subset(merged_newDGdata, `Offer Amount` == 0)

```

Sub-setting data into 3 categories: low offers, fair offers, and high offers 

```{r}

LowOfferDG = DGdata_Partitioned[DGdata_Partitioned$`Offer Amount` == c(1,2,3),]
FairOfferDG = DGdata_Partitioned[DGdata_Partitioned$`Offer Amount` == c(4,5,6),]
HighOfferDG = DGdata_Partitioned[DGdata_Partitioned$`Offer Amount` == c(7,8,9),]

LowOfferUG = UGdata_Partitioned[UGdata_Partitioned$`Offer Percentage` == c(1,2,3),]
FairOfferUG = UGdata_Partitioned[UGdata_Partitioned$`Offer Percentage` == c(4,5,6),]
HighOfferUG = UGdata_Partitioned[UGdata_Partitioned$`Offer Percentage` == c(7,8,9),]

```

Returning Average Counts for these subgroups

```{r}

MeanLowOfferDG = aggregate(x = LowOfferDG$`Dictator Accept Count`,
                           by = list(LowOfferDG$Tribe),
                           FUN = mean)
MeanFairOfferDG = aggregate(x = FairOfferDG$`Dictator Accept Count`,
                           by = list(FairOfferDG$Tribe),
                           FUN = mean)
MeanHighOfferDG = aggregate(x = HighOfferDG$`Dictator Accept Count`,
                           by = list(HighOfferDG$Tribe),
                           FUN = mean)

MeanLowOfferUG_P = aggregate(x = LowOfferUG$`Proposer Accept Count`,
                           by = list(LowOfferDG$Tribe),
                           FUN = mean)
MeanLowOfferUG_R = aggregate(x = LowOfferUG$`Responder Accept Count`,
                           by = list(LowOfferDG$Tribe),
                           FUN = mean)
MeanFairOfferUG_P = aggregate(x = FairOfferUG$`Proposer Accept Count`,
                           by = list(FairOfferDG$Tribe),
                           FUN = mean)
MeanFairOfferUG_R = aggregate(x = FairOfferUG$`Responder Accept Count`,
                           by = list(FairOfferDG$Tribe),
                           FUN = mean)
MeanHighOfferUG_P = aggregate(x = HighOfferUG$`Proposer Accept Count`,
                           by = list(HighOfferDG$Tribe),
                           FUN = mean)
MeanHighOfferUG_R = aggregate(x = HighOfferUG$`Responder Accept Count`,
                           by = list(HighOfferDG$Tribe),
                           FUN = mean)

```

Generating the graphs for the dictator game:

1. Plot of the Dictator Game when the offer amount is 0

```{r}

# Define the desired order of tribes
tribe_order_DG_f <- c("Ache", "Orma", "Tsimane", "Hadza", "Machiguenga", "Yanomami", "ChatGPT")

# Subset and reorder the data
data <- subset(DGdataZero, Tribe %in% tribe_order_DG_f)
data$Tribe <- factor(data$Tribe, levels = tribe_order_DG_f)

# Create the plot
ggplot(data, aes(x = Tribe, y = `Dictator Accept Count` )) +  
  geom_bar(stat = 'identity') +
  labs(x="",y = "Acceptance Rate") +  
  theme_bw() +
  scale_y_continuous(labels = scales::percent_format(scale = 1))  


```
2. Plot of the Dictator Game for a fair offer amount (4,5,6)
Note: The horizontal line for Base ChatGPT is derived from observing the MeanFairOfferDG dataset

```{r}

# Define the desired order of tribes
tribe_order_DG_p <- c("Ache", "Orma", "Tsimane", "Hadza", "Machiguenga", "Yanomami")

# Subset and reorder the data
data <- subset(MeanFairOfferDG, Group.1 %in% tribe_order_DG_p)
data$Group.1 <- factor(data$Group.1, levels = tribe_order_DG_p)

# Create the plot
ggplot(data, aes(x = Group.1, y = x * 10)) +  
  geom_bar(stat = 'identity') +
  geom_hline(yintercept = 2 * 10, linetype = "dashed", color = "black") +  
  annotate("text", x = Inf, y = 2.1 * 10, label = "Base ChatGPT", 
           hjust = 6.3, vjust = -0.5, color = "black") + 
  labs(x = "", y = "Acceptance Rate") +  
  theme_bw() +
  scale_y_continuous(labels = scales::percent_format(scale = 1))  

```
3. Plot of the Distribution (10%-90% offers) for the Dictator Game: Graphed by grouping tribes and their respective acceptance counts according to the offer amounts

```{r}

color_gradient_p <- c("black", "gray10", "gray15", "gray20", "gray25", "gray30", "gray40", "gray45", "gray50","gray60","gray70")

offer_labels_p <- c("10%", "20%", "30%", "40%", "50%", "60%", "70%", "80%", "90%")

ggplot(DGdata_Partitioned, aes(x = factor(Tribe, levels = tribe_order_DG_f), y = `Dictator Accept Count`, fill = factor(`Offer Amount`))) +
  geom_col(position = "dodge", width = 0.7) +  
  theme_minimal() +
  scale_fill_manual(values = color_gradient_p, labels = offer_labels_p) +  
  labs(x = "", y = "Acceptance Count",
       fill = "Offer Rate") +
  scale_x_discrete(labels = as.character(tribe_order_DG_f))

```

4. Plot of entire Distribution (0-100% offers) for the Dictator Game: Graphed by grouping tribes and their respective acceptance counts according to the offer amounts

```{r}

color_gradient_f <- c("black", "gray10", "gray15", "gray20", "gray25", "gray30", "gray40", "gray45", "gray50","gray60","gray70")

offer_labels_f <- c("0%", "10%", "20%", "30%", "40%", "50%", "60%", "70%", "80%", "90%", "100%")

ggplot(merged_newDGdata, aes(x = factor(Tribe, levels = tribe_order_DG_f), y = `Dictator Accept Count`, fill = factor(`Offer Amount`))) +
  geom_col(position = "dodge", width = 0.7) +  
  theme_minimal() +
  scale_fill_manual(values = color_gradient_f, labels = offer_labels_f) +  
  labs(x = "",
       y = "Acceptance Count",
       fill = "Offer Rate") +
  scale_x_discrete(labels = as.character(tribe_order_DG_f))  

```
Graphs for UG 

1. Distribution of Ultimatum Game for Proposer for 10%-90% offer rates

```{r}

tribe_order_UG <- c("ChatGPT", "Ache", "Orma", "Tsimane", "Hadza", "Machiguenga", "Yanomami")

# Assuming `Offer Amount` is a discrete variable, using scale_fill_manual with your colors
ggplot(UGdata_Partitioned, aes(x = factor(Tribe, levels = tribe_order_UG), y = `Proposer Accept Count`, fill = factor(`Offer Percentage`))) +
  geom_col(position = "dodge", width = 0.7) +  
  theme_minimal() +
  scale_fill_manual(values = color_gradient_p, labels=offer_labels_p) +  
  labs(x = "",
       y = "Accpetance Count",
       fill = "Offer Rate") +
  scale_x_discrete(labels = as.character(tribe_order_UG))  # Set x-axis labels to specified order

```
2. Entire distribution of Ultimatum Game for Proposer (0-100% offers)

```{r}

ggplot(UGdata, aes(x = factor(Tribe, levels = tribe_order_UG), y = `Proposer Accept Count`, fill = factor(`Offer Percentage`))) +
  geom_col(position = "dodge", width = 0.7) +  
  theme_minimal() +
  scale_fill_manual(values = color_gradient_f, labels=offer_labels_f) +  
  labs(x = "",
       y = "Acceptance Count",
       fill = "Offer Rate") +
  scale_x_discrete(labels = as.character(tribe_order_UG))  

```
3. Distribution of Ultimatum Game for Responder (10%-90% offers)

```{r}

ggplot(UGdata_Partitioned, aes(x = factor(Tribe, levels = tribe_order_UG), y = `Responder Accept Count`, fill = factor(`Offer Percentage`))) +
  geom_col(position = "dodge", width = 0.7) +  
  theme_minimal() +
  scale_fill_manual(values = color_gradient_p, labels=offer_labels_p) +  
  labs(x = "",
       y = "Acceptance Count",
       fill = "Offer Rate") +
  scale_x_discrete(labels = as.character(tribe_order_UG))  

```
4. Entire Distribution of Ultimatum Game for Responder (0-100% offers)

```{r}

ggplot(UGdata, aes(x = factor(Tribe, levels = tribe_order_UG), y = `Responder Accept Count`, fill = factor(`Offer Percentage`))) +
  geom_col(position = "dodge", width = 0.7) +  
  theme_minimal() +
  scale_fill_manual(values = color_gradient_f, labels=offer_labels_f) +  
  labs(x = "",
       y = "Acceptance Count",
       fill = "Offer Rate") +
  scale_x_discrete(labels = as.character(tribe_order_UG))  

```


